---
title: "Lab_25022022"
author: "Anish Sarkar"
date: "25/02/2022"
output: html_document
---

Tasks : 
PCA : Breast cancer dataset UCI repo
LDA : Iris
Time series: Covid-19, models : SMA, exponential moving average, ARIMA

Lab Samples : 

```{r}
#Age of Death of Successive Kings of England
#starting with William the Conqueror

# Time Series

kings <- scan("http://robjhyndman.com/tsdldata/misc/kings.dat",skip=3)
# Read 42 items
kings
kingstimeseries <- ts(kings)
kingstimeseries
#Time Series:
births <- scan("http://robjhyndman.com/tsdldata/data/nybirths.dat")
#Read 168 items
birthstimeseries <- ts(births, frequency=12, start=c(1946,1))
birthstimeseries
souvenir <- scan("http://robjhyndman.com/tsdldata/data/fancy.dat")
souvenirtimeseries <- ts(souvenir, frequency=12, start=c(1987,1))
souvenirtimeseries
plot.ts(kingstimeseries)
plot.ts(birthstimeseries)
plot.ts(souvenirtimeseries)
logsouvenirtimeseries <- log(souvenirtimeseries)
plot.ts(logsouvenirtimeseries)
#SMA - Simple Moving Average
library("TTR")
kingstimeseriesSMA3 <- SMA(kingstimeseries,n=3)
plot.ts(kingstimeseriesSMA3)
birthstimeseriescomponents <- decompose(birthstimeseries)
birthstimeseriescomponents$seasonal # get the estimated values of the seasonal component
plot(birthstimeseriescomponents)
#Forecast using Exponential smoothing
rain <- scan("http://robjhyndman.com/tsdldata/hurst/precip1.dat",skip=1)
rainseries <- ts(rain,start=c(1813))
plot.ts(rainseries)
rainseriesforecasts <- HoltWinters(rainseries, beta=FALSE, gamma=FALSE)
rainseriesforecasts
rainseriesforecasts$fitted
plot(rainseriesforecasts)
rainseriesforecasts$SSE
HoltWinters(rainseries, beta=FALSE, gamma=FALSE, l.start=23.56)
#Forecast
```

```{r}
# PCA

mtcars.pca <- prcomp(mtcars[,c(1:7,10,11)], center = TRUE,scale. = TRUE)
summary(mtcars.pca)
str(mtcars.pca)
library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
ggbiplot(mtcars.pca)
screeplot(mtcars.pca, type = "l", npcs = 15, main = "Screeplot of the first 10 PCs")
cumpro <- cumsum(mtcars.pca$sdev^2 / sum(mtcars.pca$sdev^2))
plot(cumpro[0:15], xlab = "PC #", ylab = "Amount of explained variance", main = "Cumulative variance plot")
plot(mtcars.pca$x[,1],mtcars.pca$x[,2], xlab="PC1 (44.3%)", ylab = "PC2 (19%)", main = "PC1 / PC2 - plot")
```

```{r}
# LDA

library(ggplot2)
require(MASS)
# Load data
data(iris)
head(iris, 5)
r <- lda(formula = Species ~ ., data = iris, prior = c(1,1,1)/3)
r$prior
r$counts
r$means
r$scaling
r$svd
prop = r$svd^2/sum(r$svd^2)
prop
r2 <- lda(formula = Species ~ ., data = iris, prior = c(1,1,1)/3, CV = TRUE)
head(r2$class)
head(r2$posterior, 3)
train <- sample(1:150, 75)
r3 <- lda(Species ~ ., iris, prior = c(1,1,1)/3, subset = train)
plda = predict(object = r, # predictions
newdata = iris[-train, ])
head(plda$class) # classification result
head(plda$posterior, 3)
head(plda$x, 3) # LD projections
plda_plot <- cbind(train, predict(r3)$x)
plda_df <- data.frame(plda_plot)
plda_df
# ggplot(plda_df, aes(r2, r3)) + geom_point(aes(color = Species))

```

```{r}
data(AirPassengers)
class(AirPassengers)
#This tells you that the data series is in a time series format
start(AirPassengers)
summary(AirPassengers)
edit(AirPassengers)
str(AirPassengers)
names(AirPassengers)
head(AirPassengers)
tail(AirPassengers)
library(dplyr)
glimpse(AirPassengers)
#This is the start of the time series
frequency(AirPassengers)
#The cycle of this time series is 12months in a year
summary(AirPassengers)
#The number of passengers are distributed across the spectrum
plot(AirPassengers)
#This will plot the time series
abline(reg=lm(AirPassengers~time(AirPassengers)))
#This will print the cycle across years.
cycle(AirPassengers)
plot(aggregate(AirPassengers,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(AirPassengers~cycle(AirPassengers))
#Box plot across months will give us a sense on seasonal effect
# 1. There is a trend component which grows the passenger year by year.

# 2. There looks to be a seasonal component which has a cycle less than 12 months.

# 3. The variance in the data keeps on increasing with time.
# ///adf.test(diff(log(AirPassengers)), alternative="stationary", k=0)
acf(log(AirPassengers))
pacf(diff(log(AirPassengers)))
(fit <- arima(log(AirPassengers), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 10*12)
ts.plot(AirPassengers,2.718^pred$pred, log = "y", lty = c(1,3))
```


Tasks :
1. Use Breast Cancer Wisconsin data set from the UCI Machine learning repo to plot the PCA analysis. Use the ‘prcomp’ function runs PCA on the data. 
i. You want to explain difference between malignant and benign tumors using Visualisation and add the response variable (diagnosis) to the plot 
ii. Construct some kind of model using the first 6 principal components to predict whether a tumor is benign or malignant and then compare it to a model using the original 30 variables. 
Use the below given packages to improve your results 
library(devtools) 
install_github("vqv/ggbiplot")

2. Use the built-in iris dataset in R to plot the LDA analysis. Use the lda function of the MASS package in R 
Project the LDA visual output and Compare the LDA and PCA 2D Projection of Iris dataset

Time Series Exercise Problem
 Consider the COVID-19 pandemic situation. Analysis and forecast the pandemic trend by using Covid19 dataset 
1. You want to predict the last year monthly, weekly trend based on the RTPCR response, (i.e.) No. of +Ve cases and No. –Ve cases along with admitted and discharged trend. 
2. Identify the death rate due to Covid-19 
3. Compare the last year and this year trends with respect to 1st , 2nd and 3rd wave also forecast the 4th Wave impact in India 
4. Construct the model using the Simple moving average, Exponential Moving Average and ARIMA to forecast the Covid19 Dataset. 
5. Show the all above implementation with the visual impact 

 1. Use Breast Cancer Wisconsin data set from the UCI Machine learning repo to plot the PCA analysis. Use the ‘prcomp’ function runs PCA on the data. 
i. You want to explain difference between malignant and benign tumors using Visualisation and add the response variable (diagnosis) to the plot 
ii. Construct some kind of model using the first 6 principal components to predict whether a tumor is benign or malignant and then compare it to a model using the original 30 variables. 
Use the below given packages to improve your results 
library(devtools) 
install_github("vqv/ggbiplot")

2. Use the built-in iris dataset in R to plot the LDA analysis. Use the lda function of the MASS package in R 
Project the LDA visual output and Compare the LDA and PCA 2D Projection of Iris dataset

Time Series Exercise Problem
 Consider the COVID-19 pandemic situation. Analysis and forecast the pandemic trend by using Covid19 dataset 
1. You want to predict the last year monthly, weekly trend based on the RTPCR response, (i.e.) No. of +Ve cases and No. –Ve cases along with admitted and discharged trend. 
2. Identify the death rate due to Covid-19 
3. Compare the last year and this year trends with respect to 1st , 2nd and 3rd wave also forecast the 4th Wave impact in India 
4. Construct the model using the Simple moving average, Exponential Moving Average and ARIMA to forecast the Covid19 Dataset. 
5. Show the all above implementation with the visual impact