---
title: "Social Network Analysis"
subtitle: "Reg no : 19BCE1278"
author: "Name : Anish Sarkar"
date: "Date : 07/03/2022"
output: html_document
---


```{r}
links <- read.csv("Dataset2-Media-User-Example-EDGES.csv")
nodes <- read.csv("Dataset2-Media-User-Example-NODES.csv")

links
nodes
```

```{r}
library(igraph)
mat_links <- as.matrix(links[, 2:21])
row.names(mat_links) <- links$X
mat_links
net <- graph_from_incidence_matrix(mat_links, directed = T)
plot(net, edge.arrow.size=.6, edge.curved=0,
     vertex.color="orange", vertex.frame.color="#555555",
     vertex.label=V(net)$media, vertex.label.color="black",
     vertex.label.cex=.7)
```

## 1. Read the given adjacency matrix into R

```{r}
adj_links <- get.adjacency(net)
adj_links
```

## 2. Read the given edge matrix into R

```{r}
edge_links <- get.edgelist(net, names = T)
edge_links
```

## 3. Create and plot the graph from the adjacency matrix and edge matrix (customize the vertex color edge size, vertex frame and label)

```{r}
# from adjacency matrix
net_adj <- graph.adjacency(adj_links, mode = "directed")
plot(net_adj, edge.arrow.size=.6, edge.curved=0,
     vertex.color="orange", vertex.frame.color="#555555",
     vertex.label=V(net)$media, vertex.label.color="black",
     vertex.label.cex=.7)
```



```{r}
# from edge list
net_edge <- graph.edgelist(edge_links, directed = T)
plot(net_edge, edge.arrow.size=.6, edge.curved=0,
     vertex.color="orange", vertex.frame.color="#555555",
     vertex.label=V(net)$media, vertex.label.color="black",
     vertex.label.cex=.7)
```

## 4. Display the edges & vertices, the network as matrix and the names of vertices

```{r}
E(net)
V(net)

# the network as matrix and the names of vertices
as.matrix(get.data.frame(net))
nodes$id
```

## 5. Find the count of vertices and edges of the created graph

```{r}
length(E(net))
length(V(net))
```

## 6. Display the adjacency vertices of each vertex(individual) in the created graph

```{r}
v = 1:30
v
colnames(adj_links[, 2:21])[adj_links[1, 2:21] == TRUE]
for (vertex in v) {
  adj_vert <- colnames(adj_links[, 2:21])[adj_links[vertex, 2:21] == TRUE]
  if (length(adj_vert) == 0) 
    print(0)
  else
    print(adj_vert)
}

```

## 7. Find the min and max degree of the created graph

```{r}
max(degree(net))
min(degree(net))
```

## 8. Create & set vertex attribute property named profit and values("+", "-", "+", "-", "+", "-", "+", "-", "+")

```{r}
net2 = net
profit = rep(c("+", "-"), 15)
V(net2)$profit <- profit
V(net2)
```

## 9. Create & set vertex attribute property named type and values(either leap or non-leap year)

```{r}
type <- sample(c("leap", "non-leap"), 30, replace = T)
type
V(net2)$type <- type
```

## 10. Create & set edge attribute named weight and values (if edge exits in between leap year vertices then 5 else 1 )

```{r}
type <- V(net2)$type
# length(type[type == "leap"])
index <- which(type == "leap")
index
weight <- rep(1, length(E(net2)))

E(net2)$weight <- weight

if (length(index) >= 2) {
  # for (i in index[1] : index[length(index)]) {
  #   if (V(net2)$type[i] != "leap")
  #    weight[i] = 5
  # }
}

for (i in index) {
    for (j in index) {
      if (i != j) {
        id = get.edge.ids(net2, c(V(net2)[i], V(net2)[j]), directed = T) 
        if (id != 0)
        E(net2)$weight[id] = 5
      }
    }
      
}

E(net2)$weight
```

## 11. Convert the created un-directed graph into directed graph based on the following rule
## a. edge directed towards high value vertex
## b. if any one of the vertex is leap year then put the reverse edge with same weight.

```{r}
net3 <- net2
plot(net3, vertex.label = V(net3)$profit)

# V(net3)$weight == 5
high_val <- nodes$id[V(net3)$profit == "+"]
high_val

for (i in high_val) {
  for (j in nodes$id) {
    if (i != j & !(j %in% high_val)) {
      id = get.edge.ids(net3 , c(i, j), directed = T)
      net3 <- delete_edges(net3, E(net3)[id])

    }
  }
}

E(net3)
plot(net3, vertex.label = V(net3)$profit)
```


```{r}
plot(net3)
E(net3)$weight

type_leap_nodes <- nodes$id[V(net3)$type == "leap"]
type_leap_nodes

for (node in type_leap_nodes) {
  for (vert in nodes$id) {
    if (vert != node) {
      id = get.edge.ids(net3, c(node, vert),  directed = T)
      id_rev = get.edge.ids(net3 , c(vert, node), directed = T)
      if (id != 0 & id_rev != 0) {
        E(net3)$weight[id_rev] = E(net3)$weight[id]
      }  
    }
    
  }
}

E(net3)$weight
plot(net3)
```

## 12. Display the adjacency matrix of the resultant directed graph.

```{r}
get.adjacency(net3)
```

## 13. Display the in-degree and out-degree of each vertex of resultant directed graph

```{r}
degree(net3, mode = "in")
degree(net3, mode = "out")
```

