---
title: "Time Series Analysis"
subtitle: "Reg no : 19BCE1278"
author: "Name : Anish Sarkar"
date: "Date : 03/03/2022"
output: html_document
---

# Time Series Analyis

```{r}
library(jsonlite)
library(dplyr)
data <- fromJSON("https://raw.githubusercontent.com/datameet/covid19/master/data/all_totals.json", flatten = TRUE)
```

```{r}
key_list <-data$row$key
# glimpse(data)
n <- length(unlist(key_list))

v <- c(1:n)
# v[v%%8 == 1]

dates <- unlist(key_list)[v[v%%8 == 1]]
length(dates)
```


```{r}
date <- unlist(data$rows$key)
data_csv <- data.frame(
  day_num = c(1: length(dates)),
  date = as.Date(unique(dates))
)

head(data_csv)
```


# Time Series Exercise Problem :

Consider the COVID-19 pandemic situation. Analysis and forecast the pandemic trend by using Covid19 dataset :

1. You want to predict the last year monthly, weekly trend based on the RTPCR response, (i.e.) No. of +Ve cases and No. –Ve cases along with admitted and discharged trend.

2. Identify the death rate due to Covid-19.
3. Compare the last year and this year trends with respect to 1st , 2nd and 3rd wave also forecast the 4th Wave impact in India.

4. Construct the model using the Simple moving average, Exponential Moving Average and ARIMA to forecast the Covid19 Dataset.

5. Show the all above implementation with the visual impact.


```{r}
n <- length(key_list)
v1 <- c(1:n) 
# data$rows$value[v1[v1%%4 == 1]]
data_csv$active_cases <- data$rows$value[v1[v1%%4 == 1]]
data_csv$cured <- data$rows$value[v1[v1%%4 == 2]]
data_csv$death <- data$rows$value[v1[v1%%4 == 3]]
data_csv$total_confirmed_cases <- data$rows$value[v1[v1%%4 == 0]]

tail(data_csv)
nrow(data_csv)
```

```{r}
read.csv('IndiaCovidCount.csv')
```


```{r}
# active_cases_ts <- ts(data = data_csv$active_cases, frequency = 12, start=data_csv$date[1])
active_cases_ts <- ts(data = data_csv$active_cases, start = c(2020,1,1), frequency = 365)
plot.ts(active_cases_ts)
```

1. You want to predict the last year monthly, weekly trend based on the RTPCR response, (i.e.) No. of +Ve cases and No. –Ve cases along with admitted and discharged trend.

```{r}
start <- data_csv$day_num[data_csv$date == as.Date("2021-01-01")]
end <- data_csv$day_num[data_csv$date == as.Date("2022-01-01")]
active_cases_ts <- ts(data = data_csv$active_cases[c(start:nrow(data_csv))], start = c(2021,1,1), end = c(2022, 1, 1), frequency = 365)
# active_cases_ts <- ts(data = data_csv$active_cases)
# active_cases_ts
plot.ts(active_cases_ts)
```

2. Identify the death rate due to Covid-19

```{r}
death <- abs(data_csv$death[c(2: nrow(data_csv))] - data_csv$death[c(1: (nrow(data_csv) - 1))])

deaths_ts <- ts(data = death, start = c(2020,1,30), frequency = 365)
plot.ts(deaths_ts)
```

### Death Rate

```{r}
data_csv$death[nrow(data_csv)]/data_csv$total_confirmed_cases[nrow(data_csv)]
```

### Death rate due to covid 19 in India is about 0.012.

3. Compare the last year and this year trends with respect to 1st , 2nd and 3rd wave also forecast the 4th Wave impact in India

```{r}
active_cases_ts <- ts(data = data_csv$active_cases, start = c(2020, 1, 30), frequency = 365)
forecast_covid_19 <- forecast::forecast(active_cases_ts, h=365)
plot.ts(forecast_covid_19)
plot(forecast_covid_19)
```

## According to this forecast the fourth wave of covid 19 may come between April and June of 2022.

4. Construct the model using the Simple moving average, Exponential Moving Average and ARIMA to forecast the Covid19 Dataset.

## Simple Moving Average 

```{r}
library(TTR)
active_cases_ts_SMA <- SMA(active_cases_ts, n = 20)
plot.ts(active_cases_ts_SMA)
```

## Exponential Moving Average

```{r}
library(pracma)
active_cases_ts_EMA = movavg(active_cases_ts, n = 20, type = "e")
plot.ts(active_cases_ts_EMA)
```


## ARIMA model

```{r}
# active_cases_ts <- ts(data = data_csv$active_cases, start = c(2020,1,30), frequency = 365)
active_cases_ts_log = log(active_cases_ts)
active_cases_ts_log[active_cases_ts_log == 'NaN'] = 0
plot.ts(active_cases_ts_log)

plot.ts(diff(active_cases_ts_log))
# active_cases_ts_log
acf(ts(diff(active_cases_ts_log)))
pacf(ts(diff(active_cases_ts_log)))
```

### p=0, q=1 and d=1 (differenciating once) for ARIMA(p,d,q) -> therefore order of arima = (0,1,1) 

```{r}
(fit <- arima(active_cases_ts_log, c(0, 1, 1), seasonal = list(order = c(0, 1, 1), period = 100)))
pred <- predict(fit, n.ahead = 365)
ts.plot(active_cases_ts,2.718^pred$pred, lty = c(1,3))
```

