---
title: "LAB 1"
author: "Anish Sarkar"
regno: "19BCE1278"
date: "07/01/2022"
output: html_document
---

# Name: Anish Sarkar
# Reg no: 19BCE1278
# LAB PDF Ex - 1 (Iris)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the iris dataset

```{r}
# Load the iris dataset
data("iris")
# Dimension of the iris dataset
dim(iris)
# Names of columns of the iris dataset
names(iris)
attributes(iris)
# Structure of the iris dataset
str(iris)
```

## Viewing the first 6 and last 6 data from the iris dataset 

```{r}
head(iris)
tail(iris)
```

## Looking at the first 10 values of the 'Sepal Length' attribute

```{r}
iris[1:10, "Sepal.Length"]
iris$Sepal.Length[1:10]
```

## Summary and quantile of the iris dataset

```{r}
# Summary of the iris dataset
summary(iris)
# Quantiles for the iris dataset
quantile(iris$Sepal.Length)
quantile(iris$Sepal.Length, c(.1,.3,.6))
```

## Variance of the 'Sepal Length' of the iris dataset

```{r}
var(iris$Sepal.Length)
```

## Histogram for 'Sepal Length'

```{r}
hist(iris$Sepal.Length)
```

## Density plot for 'Sepal Length'

```{r}
plot(density(iris$Sepal.Length))
```

## Pie Chart for "Species" attribute of iris dataset

```{r}
pie(table(iris$Species))
```

## Pie Chart for "Species" attribute of iris dataset

```{r}
barplot(table(iris$Species))
```

## Covariance and Correlation

```{r}
# Covariance
cov(iris$Sepal.Length, iris$Petal.Length)
cov(iris[,1:4])
# Correlation
cor(iris$Sepal.Length, iris$Petal.Length)
cor(iris[,1:4])
```

## Aggregate data from iris dataset

```{r}
a <- aggregate(Sepal.Length ~ Species, summary, data=iris)
a
```

## Boxplot

```{r}
boxplot(Sepal.Length~Species, data=iris)
```

## Plotting depicting various Species of the iris dataset

```{r}
with(iris, plot(Sepal.Length, Sepal.Width, col=Species, pch=as.numeric(Species)))
```

## Creating a pair plot

```{r}
pairs(iris)
```

## 3D scatter plot

```{r}
library(scatterplot3d)
scatterplot3d(iris$Petal.Width, iris$Sepal.Length, iris$Sepal.Width)
```

## Heat Map of iris dataset

```{r}
distMatrix <- as.matrix(dist(iris[,1:4]))
heatmap(distMatrix)
```

## Ploting contour from volcano dataset

```{r}
filled.contour(volcano, color=terrain.colors, asp=1,plot.axes=contour(volcano, add=T))
```

## Parallel Coordinates

```{r}
library(MASS)
parcoord(iris[1:4], col=iris$Species)
```

## Parallel plot

```{r}
library(lattice)
parallelplot(~iris[1:4] | Species, data=iris)
```